IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-12 assets/convergence_bcd.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,2.455in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=0,
ymax=23.9521333022272,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.9477142509994\\
3	23.9521333022272\\
4	23.9521333022272\\
5	23.9521333022272\\
6	23.9521333022272\\
7	23.9521333022272\\
8	23.9521333022272\\
9	23.9521333022272\\
10	23.9521333022272\\
11	23.9521333022272\\
12	23.9521333022272\\
13	23.9521333022272\\
14	23.9521333022272\\
15	23.9521333022272\\
};
\addlegendentry{BCD}

@@

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=0,
ymax=23.4661978529908,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.4267512312375\\
3	23.4652236267543\\
4	23.4661978529908\\
5	23.4661978529908\\
6	23.4661978529908\\
7	23.4661978529908\\
8	23.4661978529908\\
9	23.4661978529908\\
10	23.4661978529908\\
11	23.4661978529908\\
12	23.4661978529908\\
13	23.4661978529908\\
14	23.4661978529908\\
15	23.4661978529908\\
};
\addlegendentry{LC-BCD}

>>>>

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,2.455in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=0,
ymax=23.9521333022272,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.9477142509994\\
3	23.9521333022272\\
4	23.9521333022272\\
5	23.9521333022272\\
6	23.9521333022272\\
7	23.9521333022272\\
8	23.9521333022272\\
9	23.9521333022272\\
10	23.9521333022272\\
11	23.9521333022272\\
12	23.9521333022272\\
13	23.9521333022272\\
14	23.9521333022272\\
15	23.9521333022272\\
};
\addlegendentry{BCD}

@@

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=0,
ymax=23.4661978529908,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.4267512312375\\
3	23.4652236267543\\
4	23.4661978529908\\
5	23.4661978529908\\
6	23.4661978529908\\
7	23.4661978529908\\
8	23.4661978529908\\
9	23.4661978529908\\
10	23.4661978529908\\
11	23.4661978529908\\
12	23.4661978529908\\
13	23.4661978529908\\
14	23.4661978529908\\
15	23.4661978529908\\
};
\addlegendentry{LC-BCD}

### 2021-08-12 assets/convergence_sca.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,2.433in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=23.6,
ymax=24,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	23.6339898147867\\
2	23.9359168430033\\
3	23.9359212944279\\
4	23.9359212944279\\
5	23.9359212944279\\
6	23.9359212944279\\
7	23.9359212944279\\
8	23.9359212944279\\
9	23.9359212944279\\
10	23.9359212944279\\
11	23.9359212944279\\
12	23.9359212944279\\
13	23.9359212944279\\
14	23.9359212944279\\
15	23.9359212944279\\
};
\addlegendentry{SCA}

@@

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=23.1,
ymax=23.4267428478373,
ylabel style={font=\color{white!15!black}},
ylabel={DC current [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	23.1650475635163\\
2	23.4267359303359\\
3	23.4267428478373\\
4	23.4267428478373\\
5	23.4267428478373\\
6	23.4267428478373\\
7	23.4267428478373\\
8	23.4267428478373\\
9	23.4267428478373\\
10	23.4267428478373\\
11	23.4267428478373\\
12	23.4267428478373\\
13	23.4267428478373\\
14	23.4267428478373\\
15	23.4267428478373\\
};
\addlegendentry{M-SCA}

>>>>

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,2.433in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=23.6,
ymax=24,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	23.6339898147867\\
2	23.9359168430033\\
3	23.9359212944279\\
4	23.9359212944279\\
5	23.9359212944279\\
6	23.9359212944279\\
7	23.9359212944279\\
8	23.9359212944279\\
9	23.9359212944279\\
10	23.9359212944279\\
11	23.9359212944279\\
12	23.9359212944279\\
13	23.9359212944279\\
14	23.9359212944279\\
15	23.9359212944279\\
};
\addlegendentry{SCA}

@@

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=23.1,
ymax=23.4267428478373,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	23.1650475635163\\
2	23.4267359303359\\
3	23.4267428478373\\
4	23.4267428478373\\
5	23.4267428478373\\
6	23.4267428478373\\
7	23.4267428478373\\
8	23.4267428478373\\
9	23.4267428478373\\
10	23.4267428478373\\
11	23.4267428478373\\
12	23.4267428478373\\
13	23.4267428478373\\
14	23.4267428478373\\
15	23.4267428478373\\
};
\addlegendentry{M-SCA}

### 2021-08-12 assets/waveform_subband.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,3.233in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213593413934\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000411418946938571\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,2.54in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.434593216761001\\
2	4.3899297145933\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.15579196934664e-05\\
2	1.1748417131072e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,1.846in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0143736245770149\\
2	0.0303952314208929\\
3	0.115397989725443\\
4	1.83286171599636\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.03274778152889\\
2	1.26444789136652\\
3	1.50497289223671\\
4	2.05482037288244\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,1.152in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00193817595567525\\
2	0.00257713054060487\\
3	0.00348488793501541\\
4	0.00488691757665795\\
5	0.00708186101407546\\
6	0.0115819776031387\\
7	0.0297619841444503\\
8	0.248823174288891\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.958056681914786\\
2	1.1753523246861\\
3	1.34398156020033\\
4	1.48468938243277\\
5	1.59662285127524\\
6	1.68382811164256\\
7	1.75299266281476\\
8	1.84970533450897\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.438in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000699803366708424\\
2	0.000800867722584431\\
3	0.000917767493119273\\
4	0.00105546869283256\\
5	0.0012213408897823\\
6	0.00141507752657299\\
7	0.00165144517333923\\
8	0.00193060125433753\\
9	0.00227670870277157\\
10	0.0027030187224025\\
11	0.00324897530466221\\
12	0.00397867693137808\\
13	0.00501781698344776\\
14	0.00655613193903264\\
15	0.009024934371904\\
16	0.0130872335381684\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.658945444448673\\
2	0.748750326986652\\
3	0.825803524447847\\
4	0.897209109075901\\
5	0.959520330551997\\
6	1.01644204271237\\
7	1.07098120306596\\
8	1.11834785156968\\
9	1.16491430867279\\
10	1.20444111502631\\
11	1.24260696441405\\
12	1.27263946826968\\
13	1.29990806955352\\
14	1.31826230888077\\
15	1.33150577776743\\
16	1.33694997002172\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,3.21in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213593809508\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000358590327058133\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,2.522in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.550823184768846\\
2	4.36837845097092\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.48597207854411e-05\\
2	1.53805823004565e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,1.834in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0326721056203988\\
2	0.0697944085211443\\
3	0.193520763120912\\
4	1.91750698481035\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.972503011468572\\
2	1.22779327868874\\
3	1.48063097057209\\
4	2.13162879975205\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,1.146in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00676327571402152\\
2	0.00930781551713654\\
3	0.0129863266085796\\
4	0.0182780278377859\\
5	0.0264785684252956\\
6	0.0417816477229242\\
7	0.0921547943904462\\
8	0.387871897134795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.897080828535262\\
2	1.11267484124012\\
3	1.2760937466216\\
4	1.42973823824102\\
5	1.54367522426452\\
6	1.64897920494507\\
7	1.73956386270218\\
8	1.89059947472085\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00205132551819701\\
2	0.00235447373497551\\
3	0.00272196136127332\\
4	0.00316588966668174\\
5	0.00369517036368117\\
6	0.00432537450541609\\
7	0.00508695652011363\\
8	0.00600094215308655\\
9	0.00710012267822671\\
10	0.00851262778314969\\
11	0.0103510448032954\\
12	0.0128569172775466\\
13	0.0164283761517276\\
14	0.0229541038226562\\
15	0.0402894292810385\\
16	0.0926842285796484\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.628841069483884\\
2	0.717675502523908\\
3	0.795496148359302\\
4	0.864626670343281\\
5	0.930591126638763\\
6	0.989724762400551\\
7	1.04508455096183\\
8	1.09678731061405\\
9	1.14380160245268\\
10	1.18636001210616\\
11	1.2248217690153\\
12	1.2585853066132\\
13	1.28750705323146\\
14	1.31224542931104\\
15	1.33460858167442\\
16	1.35822969320702\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
